Towards more realistic model representation of microbial population dynamics in complex environment

### 2020-04-01 SI_code_revised.Rmd
Updated figures

>>>>

```{r}

fpars<-t.s6.1[c(2:4), ]
fpars$SA<-c(0, 332, 400)

fpars$Km.sd<-c(summary(two_pool_all_fixVmaxYuk_out2[[1]]$par_prof)[2,1],
               summary(two_pool_all_fixVmaxYuk_out2[[2]]$par_prof)[2,1],
               summary(two_pool_all_fixVmaxYuk_out2[[3]]$par_prof)[2,1])
fpars$fr.sd<-c(summary(two_pool_all_fixVmaxYuk_out2[[1]]$par_prof)[2,4]+
                 summary(two_pool_all_fixVmaxYuk_out2[[1]]$par_prof)[2,5],
               summary(two_pool_all_fixVmaxYuk_out2[[2]]$par_prof)[2,4]+
                 summary(two_pool_all_fixVmaxYuk_out2[[2]]$par_prof)[2,5],
               summary(two_pool_all_fixVmaxYuk_out2[[3]]$par_prof)[2,4]+
                 summary(two_pool_all_fixVmaxYuk_out2[[3]]$par_prof)[2,5])

grid.arrange(ggplot(fpars, aes(SA, Km)) + 
  geom_point(cex=6, pch=21, aes(fill = Name)) + theme_min + stat_smooth(method=lm, se = F, colour="grey30") +
  geom_errorbar(aes(ymin=Km-Km.sd, ymax=Km+Km.sd)) +
  scale_fill_manual(values=c("black", "grey", "white")) +
  xlab(expression(paste("Total surface area (", cm^{2}, ")"))) +
  ylab(expression(paste("Affinity to substrate (", mu, "mol ", L^{-1}, ")"))) +
  theme(legend.title = element_blank(),
        legend.position = c(0.75, 0.75))+
  ggtitle("A)"), 
  ggplot(fpars, aes(SA, fpr+fps)) + 
  geom_point(cex=6, pch=21, aes(fill = Name), show.legend = F) + theme_min + stat_smooth(method=lm, se = F, colour="grey30") +
  geom_errorbar(aes(ymin=fpr+fps-fr.sd, ymax=fpr+fps+fr.sd)) +
  scale_fill_manual(values=c("black", "grey", "white")) +
  xlab(expression(paste("Total surface area (", cm^{2}, ")"))) +
  ylab("Abundance of proteins in cells") + ggtitle("B)"),
  nrow=1)

```{r}
source("./Rscripts/two_pool_plot.R")

sim_out<-two_pool_plot(fpars)

bplot<-m0 %>% filter(Substrate=="Glucose" | Substrate=="Cellobiose") %>% 
  group_by(Structure, Substrate, Day) %>%
  summarise(P = mean(Prot.in*0.46/12.01/4, na.rm=T),
            P.sd = sd(Prot.in*0.46/12.01/4, na.rm=T),
            D = mean(DNA*0.51/12.01/4, na.rm=T),
            D.sd = sd(DNA*0.51/12.01/4, na.rm=T)) 
bplot$Struc<-NA

for(i in 1:nrow(bplot)){
  if(bplot$Structure[i]=="Broth"){
    bplot$Struc[i]<-"BROTH"
  }else{
    if(bplot$Structure[i]=="Glass wool"){
      bplot$Struc[i]<-"WOOL"
    }else{
      bplot$Struc[i]<-"GLASS"
    }
  }
}

bplot$Struc<-factor(bplot$Struc, levels=c("BROTH", "GLASS", "WOOL"))

ggplot(bplot, aes(x=Day*24))+
    geom_point(cex=6, aes(y=P, colour="Cellular Proteins", shape=Substrate)) +
  geom_errorbar(aes(ymin=P-P.sd, ymax=P+P.sd, color="Cellular Proteins"), width=0.0001, lwd=1)+
  geom_line(data = sim_out, aes(x=time, y=Protc, colour="Cellular Proteins"), lwd=1.5)+
    geom_point(cex=6, aes(y=D*28, colour="DNA", shape=Substrate))+
  geom_errorbar(aes(ymin=(D-D.sd)*28, ymax=(D+D.sd)*28, color="DNA"), width=0.0001, lwd=1)+
  geom_line(data = sim_out, aes(x=time, y=DNAc*28, colour="DNA"), lwd=1.5)+
    scale_y_continuous(sec.axis = sec_axis(~./28, 
                       name = expression(paste("DNA (", mu ,"mol(",C[DNA],")" ,ml^{-1}, ")"))), limits = c(0, 3))+
    scale_colour_manual(values = c( "black", "grey60"))+
    labs(y = expression(paste("Cellular Proteins (", mu ,"mol(",C[Proteins],")" ,ml^{-1}, ")")),
         x = "Time (h)")+
    theme_min + facet_wrap(~Struc, ncol=1) + expand_limits(x = 0, y = 0) +
  theme(legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.spacing.y = unit(2.6, "in"),
        legend.spacing.x = unit(0.05, "in"),
        legend.position = c(0.65, 0.45),
        legend.background = element_blank(),
        )

source("./Rscripts/monod_plot.R")
sim_monod_out<-monod_plot(t.s4.1)

bplot$Struc<-factor(bplot$Struc, levels=c("BROTH", "GLASS", "WOOL"))

ggplot(bplot, aes(x=Day*24))+
    geom_point(cex=6, aes(y=P, colour="Cellular Proteins", shape=Substrate)) +
  geom_errorbar(aes(ymin=P-P.sd, ymax=P+P.sd, color="Cellular Proteins"), width=0.0001, lwd=1)+
  geom_line(data = sim_out, aes(x=time, y=Protc, colour="Cellular Proteins"), lwd=1.5)+
  geom_line(data = sim_monod_out, aes(x=time, y=Protc, colour="Cellular Proteins"), lwd=1, linetype="dashed")+
    geom_point(cex=6, aes(y=D*28, colour="DNA", shape=Substrate))+
  geom_errorbar(aes(ymin=(D-D.sd)*28, ymax=(D+D.sd)*28, color="DNA"), width=0.0001, lwd=1)+
  geom_line(data = sim_out, aes(x=time, y=DNAc*28, colour="DNA"), lwd=1.5)+
  geom_line(data = sim_monod_out, aes(x=time, y=DNAc*28, colour="DNA"), lwd=1, linetype="dashed")+
    scale_y_continuous(sec.axis = sec_axis(~./28, 
                       name = expression(paste("DNA (", mu ,"mol(",C[DNA],")" ,ml^{-1}, ")"))), limits = c(0, 3))+
    scale_colour_manual(values = c( "black", "grey60"))+
    labs(y = expression(paste("Cellular Proteins (", mu ,"mol(",C[Proteins],")" ,ml^{-1}, ")")),
         x = "Time (h)")+
    theme_min + facet_wrap(~Struc, ncol=1) + expand_limits(x = 0, y = 0) +
  theme(legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.spacing.y = unit(2.6, "in"),
        legend.spacing.x = unit(0.05, "in"),
        legend.position = c(0.65, 0.45),
        legend.background = element_blank(),
        )

ggplot(sim_out, aes(x=time))+
    geom_line(lwd=1.5, aes(y=Protc/(R+S)*100, colour="Cellular Proteins")) +
    geom_line(lwd=1.5, aes(y=DNAc/(R+S)*15*100, colour="DNA"))+
    scale_y_continuous(sec.axis = sec_axis(~./15, 
                       name = expression(paste(frac(C[DNA], Biomass)%*%100))))+
    scale_colour_manual(values = c( "black", "grey60"))+
    labs(y = expression(paste(frac(C[Proteins], Biomass)%*%100)),
         x = "Time (h)")+
    theme_min + facet_wrap(~Struc, ncol=1) + expand_limits(x = 0, y = 0) +
  theme(legend.title = element_blank(),
        legend.direction = "horizontal",
        legend.spacing.y = unit(2.6, "in"),
        legend.spacing.x = unit(0.05, "in"),
        legend.position = c(0.55, 0.45),
        legend.background = element_blank(),
        )
